\documentclass[12pt]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\linespread{1}
\pagestyle{empty}
\setlength\parindent{12pt}


\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\title{6.852 Distributed Algorithms Project Outline}
\author{Ariel Anders and Noel Hollingsworth}

\begin{document}
\begin{center}{\bf \Large
6.852 Distributed Algorithms Project Outline\\ }
Ariel Anders and Noel Hollingsworth 
\\
{\bf \em Decentralized Approaches for Autonomous Intersection Control }
\end{center}
\begin{itemize}
\item Introduction
	\begin{itemize}
		\item Motivation  
		\item Problem Definition\\
		Mutual exclusion problem- only one car allowed in the critical region (intersection)\\
		What assumptions are we making about the cars? (message passing capabilities)\\
		How are we defining a successful algorithm?  throughput, wait-free\\
	\end{itemize}
\item Decentralized Approaches  \\ 
Translate these algorithms into distributed algorithms lingo
\begin{itemize}
	\item Ring based semaphore control \cite{naumann}
	\item Decentralized Navigation Functions \cite{roozbehani}\\
	This paper has been built upon.  \cite{makarem} modifies it in such a way that heavier vehicles that need more energy and time for acceleration or breaking are given an indirect priority at intersections etc.
	\item Virtual Node Layer Approach \cite{vnlayer}
\end{itemize}
\item Future Work Discussion
	\begin{itemize}
		\item Try to use VNLayer to use a centralized algorithm (such as  \cite{dresner})
		\item Discussion on different areas to optimize for these algorithms.  This could include different levels of priority for cars and different measures for throughput.
	\end{itemize}
\item Conclusion
\end{itemize}

\begin{thebibliography}{9}

\bibitem{vnlayer}
Brown, Matthew, et al. "The virtual node layer: a programming abstraction for wireless sensor networks." SIGBED Review 4.3 (2007): 7-12.

\bibitem{naumann}
Naumann, Rolf, and Rainer Rasche. ``Intersection collision avoidance by means of decentralized security and communication management of autonomous vehicles", Univ.-GH, SFB 376, 1997.

\bibitem{roozbehani}
Roozbehani, Hajir, Sylvain Rudaz, and Denis Gillet. "On decentralized navigation schemes for coordination of multi-agent dynamical systems." Systems, Man and Cybernetics, 2009. SMC 2009. IEEE International Conference on. IEEE, 2009.

\bibitem{makarem}
Makarem, Laleh, and Denis Gillet. "Decentralized Coordination of Autonomous Vehicles at intersections." World Congress. Vol. 18. No. 1. 2011.

\bibitem{dresner}
Kurt Dresner and Peter Stone. ''Multiagent Traffic Management: An Improved Intersection
Control Mechanism", AAMAS'05 Proceedings of the fourth international joint conference on Autonomous agents and multiagent systems, New York, NY, USA, 2005.
\end{thebibliography}



\end{document}
